\section{Baseline Model}
\label{sec:baseline_model}

To analyse the macroeconomic effects of financial shocks, \citeauthor{JERMANNfinancial} first employ an augmented version of the canonical real business cycle model. Based on the empirical findings above, they model firm financing as a trade off between debt and equity. In the model, firms prefer debt to equity. \citeauthor{JERMANNfinancial} incorporate this pecking order by assuming that debt financing is linked to a tax benefit. In addition, firms may endogenously default on their obligations from intraperiod loans and intertemporal debt. In case of default, only the firms' physical capital is assumed to be available for liquidation. By adding uncertainty about the future liquidation value of physical capital, \citeauthor{JERMANNfinancial} introduce the basis for financial shocks to the RBC model. In this framework, the probability of the lender receiving the full value of future physical capital is determined by market conditions. This probability is stochastic and directly affects a firm's ability to borrow. Hence, the random disturbances it is subject to can be interpreted as financial shocks. The financial shocks are complemented by productivity shocks measured as Solow residuals from the production function.


\subsection{Shock Construction}
\label{sec:shock_construction}

\input{figures/replication_figure_2}

The replication of Figure \ref{fig:figure_2} is based on the updated data from the FFA, NIPA and Current Employment Statistics (CES) from the Bureau of Labor Statistics (BLS). The procedure employed to construct the shock series generally follows the steps as outlined by \citeauthor{JERMANNfinancial}. However, some steps have been corrected or adjusted in the calculation of the productivity shocks. These deviations will be addressed in the following. 

First, the value for initial capital is set to $22.53$ such that there is no trend in the ratio of capital to real business gdp for the updated capital series. Second, the online appendix indicates that the capital stock is calculated using the equation
\begin{equation} 
	\label{eq:capital_online_appendix}
	k_{t+1} = k_{t} - Depreciation + Investment.
\end{equation} 
Thus, ${k}_t$ denotes the capital at the end of period $t-1$. However, the timing \citeauthor{JERMANNfinancial} employ in the construction of the productivity shocks contradicts equation (\ref{eq:capital_online_appendix}). More specifically, they calculate the shocks using next period's capital stock. In the replication, the construction of shocks adheres to the timing convention as specified by equation (\ref{eq:capital_online_appendix}). That is, productivity shocks in the current quarter are calculated using last quarter's end of period capital stock. Third, following the description in the online appendix, the productivity shocks used to replicate Figure \ref{fig:figure_2} are based on business GDP. The original data set, however, reveals that \citeauthor{JERMANNfinancial} use real GDP instead. 

The resulting series of shocks shown in Figure \ref{fig:figure_2} exhibit patterns similar to the ones from the original paper. However, the estimates for matrix $A$ contained in Appendix \ref{sec:appendix_shock_construction} indicate that the off-diagonal elements of $A$ are strongly influenced by the corrections described above and in particular by the choice of GDP. In addition, Figure \ref{fig:residual_autocorrelation} shows that there is significant autocorrelation present in ${\epsilon}_{\xi,t+1}$ when considering the first to third lag. Moreover, there is a correlation of $0.6960$ between the residuals. Together, these findings imply that the residuals in the VAR model do not resemble white noise. As a consequence, the model is most likely misspecified.


\subsection{Findings}
\label{sec:findings}

\input{figures/replication_figure_5}

Figure \ref{fig:figure_5} compares the empirical series of output, working hours and financial flows to the simulated series obtained from the model in response to both shock series estimated above. More specifically, the graph shows the proportional deviations from the respective steady state values. To create empirical series of proportional deviations, the observations need to be detrended and centred around zero. Following the procedure by \citeauthor{JERMANNfinancial}, taking the logarithm of real GDP from the NIPA (Table 1.1.6.) and linearly detrending the resulting series over the period 1984:I--2015:III yields output as shown in Figure \ref{fig:figure_5}. The same procedure is applied to the index of aggregate weekly hours from the CES. Debt and equity payouts are obtained by linearly detrending the data series described in section \ref{sec:data}. While the scales differ for output and hours, the resulting figure generally replicates the dynamics as illustrated by Figure 5 in the original paper.
