\section{Extended Model}
\label{sec:extended_model}

The second approach \citeauthor{JERMANNfinancial} employ to analyse the macroeconomic effects of financial shocks is based on the model estimated by \citet{SMETSshocks}. In particular, they extend this model by including financial shocks and financial frictions as introduced in section \ref{sec:baseline_model}. This allows them to assess the impact of financial shocks relative to other sources of shocks. 

In contrast to the baseline model, the extended model includes a public sector. Public policy in this model comprises both monetary policy and fiscal policy. Monetary policy is determined by a Taylor rule. At the same time, government purchases and interest deduction are financed with lump-sum taxes. The second major deviation from the baseline model are nominal rigidities in wages and prices. Building on the New Keynesian literature, \citeauthor{JERMANNfinancial} incorporate an explicit wage and price setting mechanism of households and firms. By making use of Calvo's price rigidity, they obtain wage rigidities. To generate nominal price rigidities, they employ Rotemberg's approach, which is based on convex price adjustment costs.


\subsection{Estimation of the Extended Model}
\label{sec:extended_model_estimation}

\input{tables/replication_table_3}

The replication of Table 3 from the original paper summarised in Table \ref{tab:table_3} is based on the original data set provided by \citeauthor{JERMANNfinancial}. It contains eight empirical series, namely: GDP, personal consumption expenditures, investment, inflation, federal funds rate, debt repurchases of nonfinancial businesses, working hours, and hourly wages. However, to match the empirical series to their theoretical counterparts, the observations need to be transformed prior to the estimation. In particular, estimating the model requires growth rates of the following series: GDP, consumption, investment, price deflator, working hours and wages. Therefore, I first take log-differences of the series above and demean the resulting series. Given that the federal funds rate is expressed in percentage terms, the original series only needs to be demeaned without taking log-differences. Following the procedure employed in section \ref{sec:baseline_model} for Figure \ref{fig:figure_5}, debt repurchases are linearly detrended.\footnote{Note that debt repurchases as shown in Figure \ref{fig:figure_1} do not seem to have a trend. Hence, linearly detrending the series does not yield significantly different results compared to demeaning it.}

Note that the prior distributions for the average price markup $\bar{\eta}$ and the average wage markup $\bar{\upsilon}$ in Table \ref{tab:table_3} are generalised beta distributions with support [1, 2].


\subsection{Convergence}
\label{sec:convergence}

This section assesses the convergence of the Markov Chain Monte Carlo simulation from section \ref{sec:extended_model_estimation}. For this purpose, Figure \ref{fig:convergence} in Appendix \ref{sec:appendix_convergence} contains trace plots for the estimated variances of the productivity shocks $z$ and the financial shocks $\xi$. The simulation is conducted using $3\times10^{6}$ iterations. In the figure, moving averages are calculated over $3\times10^{5}$ sampled values. While the variance of the productivity shocks seems to be convergent, the variance of the financial shocks displays signs of metastability. Metastability describes situations in which Markov chains appear to have converged. However, after a potentially large number of iterations, the chain starts moving to a different region of the parameter space \citep{PATILpymc}. Consequently, this behaviour cannot be detected when setting the number of iterations to $10^{4}$ from the original paper as the break takes place after approximately $2\times10^{6}$ iterations. A more formal measure is given by the convergence diagnostic proposed by \cite{GEWEKEevaluating}. Based thereon, the p-values of chi squared tests for equality of means from the beginning and end of the chain are calculated by Dynare. For both variances, the p-values are smaller than $0.05$. Thus, the null hypothesis of convergence can be rejected at the 5\% level.
